---
title: "Presentation Ninja"
subtitle: "&#x2694;&#xFE0F; xaringan +<br/>&#x1F60E; xaringanthemer"  
author: 
  - "Yihui Xie"
  - "Garrick Aden-Buie"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    seal: false
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  fig.show = TRUE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#e3f1e6",
  secondary_color = "#274247",
  inverse_header_color = "#FFFFFF",
  header_color = "#274247",
  background_color = "#e3f1e6"
)
```

```{r xaringan-logo, echo=FALSE}
xaringanExtra::use_logo(
  image_url = "pictures/ssb-logo-rgb300pxl.png", position=xaringanExtra::css_position(top="1em", right="1em")
)
```

## Forberedelser til DAPLA-overgang

.pull-left[

### Agenda

1. Linux

2. GIT 

3. IDE

4. Markdown

5. Visualiseringer

]

.pull-right[

<br> 

<pre style="font: 4px/2px monospace;">@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@#O$%%??%%$O#@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@&$?eoii==========iioe?$&@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@O?*i==+++;;;;;;;;;;;;+++==i*?O@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@#!oi=++;;:::::_______::::::;;++=io!#@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@$*i=++;::::__________________:::;;++=i*%@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@@@@@@@@@@%o==+;;:::______-----------_______:::;;+=io%@@@@@@@@@@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@@@@@@@@%o==+;;::______-----------------______:::;;+=io%@@@@@@@@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@@@@@@O*i=+;;::_____-----------------------_____:::;;+=i*O@@@@@@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@@@@&?i=+;;:::_____-------------------------_____:::;;++=i!&@@@@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@@@Oo==+;;:::____----------------------------_____::::;;+=ioO@@@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@@%i=++;:::______-----------------------------______:::;;++=i%@@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@!i=+;;::::______-----------------------------_______:::;;++=i!@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@&*i=+;;::::______------------------------------_______::::;;++=i*&@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@#*==+;;::::_______------------------------------________::::;;++=i*#@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@#o==+;;;:::________-----------------------------_________:::::;;++==o#@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@#o==+;;;::::________-----------------------------_________:::::;;;++==o#@@@@@@@@@@@@@@
@@@@@@@@@@@@@&*==++;;:::::__________--------------------------__________::::::;;;++==*&@@@@@@@@@@@@@
@@@@@@@@@@@@&*i=++;;;:::::____________------------------________________::::::;;;+++=i*@@@@@@@@@@@@@
@@@@@@@@@@@@!i=+++;;::::::______________________________________________::::::;;;;+++=i!@@@@@@@@@@@@
@@@@@@@@@@@%i=+++;;;:::::::____________________________________________:::::::;;;;++++=i%@@@@@@@@@@@
@@@@@@@@@@Oi=++++;;;:::::::____________________________________________:::::::;;;;;+++==iO@@@@@@@@@@
@@@@@@@@@&*==+++;;;;::::::::__________________________________________:::::::::;;;;++++=i*&@@@@@@@@@
@@@@@@@@@!i=++++;;;;:::::::::_______________________________________::::::::::;;;;;+++++=i?@@@@@@@@@
@@@@@@@@#i=+++++;;;;::::::::::::________________________________::::::::::::::;;;;;;++++==iO@@@@@@@@
@@@@@@@@*i=++++;;;;;::::::::::::::::::::::::::::::::::::::::::::::::::::::::::;;;;;++++++=i*@@@@@@@@
@@@@@@@$i=+++++;;;;;;::::::::::::::::::::::::::::::::::::::::::::::::::::::::;;;;;;++++++==i$@@@@@@@
@@@@@@@*==+++++;;;;;;;:::::::::::::::::::::::::::::::::::::::::::::::::::::::;;;;;;+++++++=io@@@@@@@
@@@@@@%i=++++++;;;;;;;::::::::::::::::::::::::::::::::::::::::::::::::::::::;;;;;;;+++++++==i%@@@@@@
@@@@@@*==+++++++;;;=i*ee!ee*o=+::::::::::::::::::::::::::::::::::::::;=o*e!!!e*i=;;++++++++=io@@@@@@
@@@@@$i==+++++ie%O&@@@@@@@@@@@@&#$?*i;:::::::::::::::::::::::::;=o!$#@@@@@@@@@@@@&O%!o=++++==i$@@@@@
@@@@@ei==i*?O&@@@@@@@@@@@@@@@@@@@@@@@@#%*=;::::;;;;;;;;:::;=*?$&@@@@@@@@@@@@@@@@@@@@@@@O!o===i*@@@@@
@@@@#iiO&@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@&O?eoi=++==o*!%O@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@&O?=i#@@@@
@@@@?io@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@oi?@@@@
@@@@oio@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@oio@@@@
@@@#i=o@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@i=iO@@@
@@@?i==@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@o=i?@@@
@@@ei==$@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@i=i*@@@
@@&o====#@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@#o==io&@@
@@Oi===+i&@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@&&@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@o+===i$@@
@@%i===++*@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@#=+++e@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@%++===i?@@
@@!i===+++#@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@*+++++?@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@*++===ie@@
@@*i==++++%@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@&++++++=@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@&=++===i*@@
@@oi===+++*@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@%+++++++$@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@$+++===io@@
@#oi===+++=@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@*+++++++e@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@!+++===io#@
@Oo====++++O@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@=+++++++=@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@i++====ioO@
@Oi====++++!@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@O+++++++++O@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@&+++=====i$@
@$i====++++i@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@e+++++++++*@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@$+++=====i$@
@%i====+++++O@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@#+++++++++++&@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@e+++=====i%@
@%i=====++++e@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@e+++++++++++!@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@=++======i?@
@%i======+++=&@@@@@@@@@@@@@@@@@@@@@@@@@@@@@O++++++++++++=&@@@@@@@@@@@@@@@@@@@@@@@@@@@@@$++=======i?@
@%i======++++%@@@@@@@@@@@@@@@@@@@@@@@@@@@@@o+++++++++++++e@@@@@@@@@@@@@@@@@@@@@@@@@@@@@*++======ii%@
@$ii======+++o@@@@@@@@@@@@@@@@@@@@@@@@@@@@?+++++++++++++++O@@@@@@@@@@@@@@@@@@@@@@@@@@@O++=======ii%@
@Ooi======++++O@@@@@@@@@@@@@@@@@@@@@@@@@@O++++++++++++++++=&@@@@@@@@@@@@@@@@@@@@@@@@@&i++=======io$@
@Ooi=======+++o@@@@@@@@@@@@@@@@@@@@@@@@@#=+++++++++++++++++i&@@@@@@@@@@@@@@@@@@@@@@@@*++========ioO@
@#oi=======++++e@@@@@@@@@@@@@@@@@@@@@@@#i+++++++++++++++++++i&@@@@@@@@@@@@@@@@@@@@@@e++=========io#@
@@oi========++++*&@@@@@@@@@@@@@@@@@@@@O=+++++++++++++++++++++=$@@@@@@@@@@@@@@@@@@@#o+++=========io@@
@@*i=========++++=?&@@@@@@@@@@@@@@@@&!+++++++++++++++++++++++++*O@@@@@@@@@@@@@@@&?=+++==========i*@@
@@!i=========++++++=e$&@@@@@@@@@@@O!=++++++++++++++++++++++++++++i?#@@@@@@@@@&$e=++++===========ie@@
@@%ii=========+++++++++oe!?%%??eo=++++++++++++++++++++++++++++++++++=oe!??!eo=+++++++==========ii?@@
@@Ooi===========+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++============io$@@
@@&oi===========++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++=============io&@@
@@@ei============++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++=============ii*@@@
@@@?ii============+++++++e++++++++++++++++++++++++++++++++++++++++++++++++o++++++=============ii?@@@
@@@#oi==============+++++%o++++++++++++++++++++++++++++++++++++++++++++++=?++++===============ioO@@@
@@@@*ii==============++++!%=+++++++++++++++++++++++++++++++++++++++++++++!?+++===============iio@@@@
@@@@?ii===============+++*$?=+++++++++++++++++++++++++++++++++++++++++++*$*++================ii?@@@@
@@@@#oi=================+=%%!=+++++++++++++++++++++++++++++++++++++++++*$$=+=================io#@@@@
@@@@@eii=================+e%%?=+++++++++++++++++++++++++++++++++++++++*%%!==================ii*@@@@@
@@@@@$oi===================??%?i++++++++++++++++++++++++++++++++++++=e?%%i==================io$@@@@@
@@@@@@*ii==================o???%e=+++++++++++++++++++++++++++++++++o!??%*==================ii*@@@@@@
@@@@@@%oi===================*!!???*=+++++++++++++++++++++++++++++ie!!??e===================io%@@@@@@
@@@@@@@*ii===================*!!!???*=++++++++++++++++++++++++=oe!!!!!e===================ii*&@@@@@@
@@@@@@@$oi====================oee!!???!*=++++++++++++++++++=o*!!eee!!*===================iio$@@@@@@@
@@@@@@@@eii====================ieee!!!!??!e*oi=++++++=iio*e!eeeeeee!o====================ii*@@@@@@@@
@@@@@@@@#oii=====================oeeeee!!!!!????!!!!!!!!!eeeeeeeee*i====================iioO@@@@@@@@
@@@@@@@@@?oii======================oe*eeeeeeeeeeeeeeeeeeee*****e*i=====================iio?@@@@@@@@@
@@@@@@@@@&*ii========================o*********ee************eoi======================iii*&@@@@@@@@@
@@@@@@@@@@Ooii=========================io******************oi=========================iioO@@@@@@@@@@
@@@@@@@@@@@%oii============================iioooo***oooii============================iio%@@@@@@@@@@@
@@@@@@@@@@@@!oii====================================================================iio!@@@@@@@@@@@@
@@@@@@@@@@@@&eiii==================================================================iiie@@@@@@@@@@@@@
@@@@@@@@@@@@@&*iii================================================================iii*&@@@@@@@@@@@@@
@@@@@@@@@@@@@@&*iii==============================================================iii*#@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@#*iii============================================================iii*#@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@&*iii==========================================================iii*&@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@&eoii========================================================iioe&@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@&!oiii====================================================iiio!&@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@@%oiii==================================================iiio%@@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@@@O*oiii==============================================iiio*O@@@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@@@@&?oiiii==========================================iiiio?&@@@@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@@@@@@Oeoiiii======================================iiiioe#@@@@@@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@@@@@@@@$*oiiii==================================iiiio*$@@@@@@@@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@@@@@@@@@@%*oiiiii============================iiiiio*%@@@@@@@@@@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@$eoiiiiiii====================iiiiiiioe$@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@#?*oiiiiiiiiiii======iiiiiiiiiiio*?#@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@#?eooiiiiiiiiiiiiiiiiiiiiooe?O@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@&O%!*ooooooiioooooo*!%O&@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@#OO$%%%%$OO#@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
</pre>

]